### 2022-05-18 main/chapter_2ljets.tex
tweaks; add 2ljets references

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_summary_log.pdf}
\caption{%
Data of the $\twoljets$ electroweak analysis with \emph{post-fit} backgrounds
for which the lower panel shows $S_\mathrm{ATLAS}$ from
Equation~\ref{eqn:significance_atlas}.
Control, validation and signal regions are shown from left to right, with the
regions within each category ordered approximately by their typical $\met$.
Likelihoods from validation regions are not included in the fit.
The `Top' category contains $t\bar t$ and $tW$ processes, and
`Other' contains fake/non-prompt lepton, higgs, triboson, $t\bar tZ$, and other
rare top processes.%
}
\label{fig:2ljets_summary}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{figures/2ljets_c1n2_llqqn1n1_wz.pdf}
\hfill
\includegraphics[width=0.45\textwidth]{figures/2ljets_n1n1_hhggzz.pdf}
\caption{%
Supersymmetric signal processes in the $\twoljets$ electroweak analysis.
\\[0.5em]
Left: C1N2, where the initial $\chargino{1}\textrm{--}\neutralino{2}$ pair
is produced through a $s$-channel $W^{\pm}$ resonance and the masses of
weak bosons in decays are bounded by the mass splitting
$m(\chargino{1}, \neutralino{2}) - m(\neutralino{1})$.
We explore the parameters
$m(\chargino{1}, \neutralino{2})$ and $m(\neutralino{1})$.
\\[0.5em]
Right: GMSB, where the initial $\neutralino{1}\textrm{--}\neutralino{1}$ pair
is produced by soft decays from pairs including $\chargino{1}$,
$\neutralino{2}$ or $\neutralino{1}$.
Although the $h$ and $Z$ bosons decay to many states, we target
$Z\rightarrow \ell\ell$ with
$h/Z\rightarrow bb/jj$.
We explore the parameters
$m(\neutralino{1})$ and $B(\neutralino{1} \rightarrow h \tilde{G})$ with fixed
$m(\chargino{1}, \neutralino{2}) - m(\neutralino{1}) = 1~\eV[G]$.
}
\label{fig:2ljets_signal_diagrams}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_sr_high_8_met_sig.pdf}
    \caption{SR-High-8}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_sr_llbb_mbb.pdf}
    \caption{SR-$\ell\ell bb$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_sr_int_met_sig.pdf}
    \caption{SR-Int}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_sr_low_met_sig.pdf}
    \caption{SR-Low}
\end{subfigure}
\caption{%
Example signal region histograms with benchmark signal sample yields overlaid
as dotted lines.
Physically, signal yields would add on top of the backgrounds.
Data are shown; regions in the the top two plots observe zero data, and the
Poisson error bars for $0$ events are hidden for aesthetic reasons.
}
\label{fig:2ljets_signal_examples}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/2ljets_contours_c1n2.pdf}
\caption{%
Contours for the C1N2 model in the $\twoljets$ electroweak analysis.
Space below the solid red line is labelled as excluded and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
The yellow band shows the $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the prior distribution of the test statistic.
Grey areas are observed limits from the two-lepton parts
of~\cite{atlas_23l_SUSY_2016_24} and~\cite{atlas_2l_SUSY_2013_11}.
Exclusion is defined by the $95\%$ $\mathrm{CLs}$ prescription
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours_c1n2}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/2ljets_contours_gmsb.pdf}
\caption{%
Contours for the GMSB model in the $\twoljets$ electroweak analysis.
Space below the solid red line is labelled as excluded and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
The yellow band shows the $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the prior distribution of the test statistic.
Exclusion is defined by the $95\%$ $\mathrm{CLs}$ prescription
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours_gmsb}
\end{figure}

% upper limits
% definitely want this after pictures
\FloatBarrier
\begin{table}[tp]
\centering
% custom separator for aligned +-
% https://stackoverflow.com/a/2132998
\begin{tabular*}{\textwidth}{lr@{$~\pm~$}lccrrcc}
Region &
\multicolumn{2}{c}{Fitted} &
Data &
$\langle A\epsilon{ \sigma}\rangle_{\mathrm{obs}}^{95}~\mathrm{fb}$ &
$S_{\mathrm{obs}}^{95}$  &
$S_{\mathrm{exp}}^{95}$ &
$\mathrm{CLb}$ &
$p(s=0)$  \\[1.5ex]
DR-OffShell      & $22.1$ & $2.7$ & 21 & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50$ \\[.5ex]
DR-Low           & $22$ & $4$ & 18 & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50$ \\[.5ex]
DR-Int           & $35$ & $4$ & 38 & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23$ \\[.5ex]
DR-High          & $3.9$ & $0.5$  & 0  & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0.00$ & $0.50$ \\[.5ex]
DR-$\ell\ell bb$ & $0.51$ & $0.20$  & 0  & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50$ \\[.5ex]
\end{tabular*}
\caption{%
Upper limit results in discovery region.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right:
the region name,
the post-fit background expectation,
the number of data observed,
the observed $95\%$ $\mathrm{CLs}$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
the expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central or
$\pm1$-sigma variations,
$\mathrm{CLb}$ evaluated with the signal expectation set to the observed upper limit,
and the discovery $p$-value (capped at $0.5$) with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test statistic.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided test.
All $p$-values are estimated by simulation of alternative data.
\TODO{add labels and references to asymptotic formulae paper}
\TODO{reference pdg rounding}
}
\label{tab:2ljets_discovery}
\end{table}

@@

Unsurprisingly, the strong part of the $\twoljets$ analysis,
detailed in Section~\ref{sec:2ljets_origins_strong},
searches for effects from the strong sector.
It also uses conventional event variables and with an emphasis on the mass
spectrum of lepton pairs.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/2ljets_rjr_trees.pdf}
\caption{%
Decay trees for the $\twoljets$ RJR analysis.
Both diagrams represent processes also targetted in the electroweak analysis.
(left) A fully-resolved decay tree with its particles labelled.
(right) Only the $Z\rightarrow\ell\ell$ (\underline{v}ector boson)
is resolved, but the supersymmetric system recoils off
hard QCD jets labelled ``ISR'', boosting the \underline{i}nvisible particles,
to generate visibly large $\met$ in models with small mass-splittings.
The same approach is used for SR-OffShell selections in the electroweak
analysis.
\emph{This figure was made by the RJR team.}
}
\label{fig:2ljets_rjr_decay_trees}
\end{figure}

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_summary_log.pdf}
\caption{%
Data of the $\twoljets$ electroweak analysis with \emph{post-fit}
backgrounds~\cite{atlas2022searches}.
The lower panel shows $S_\mathrm{ATLAS}$ from
Equation~\ref{eqn:significance_atlas}.
Control, validation and signal regions are shown from left to right, with the
regions within each category ordered approximately by their typical $\met$.
Likelihoods from validation regions are not included in the fit.
The `Top' category contains $t\bar t$ and $tW$ processes, and
`Other' contains fake/non-prompt lepton, higgs, triboson, $t\bar tZ$, and other
rare top processes.%
}
\label{fig:2ljets_summary}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{figures/2ljets_c1n2_llqqn1n1_wz.pdf}
\hfill
\includegraphics[width=0.45\textwidth]{figures/2ljets_n1n1_hhggzz.pdf}
\caption{%
Supersymmetric signal processes in the $\twoljets$ electroweak
analysis~\cite{atlas2022searches}.
\\[0.5em]
Left: C1N2, where the initial $\chargino{1}\textrm{--}\neutralino{2}$ pair
is produced through a $s$-channel $W^{\pm}$ resonance and the masses of
weak bosons in decays are bounded by the mass splitting
$m(\chargino{1}, \neutralino{2}) - m(\neutralino{1})$.
We explore the parameters
$m(\chargino{1}, \neutralino{2})$ and $m(\neutralino{1})$.
\\[0.5em]
Right: GMSB, where the initial $\neutralino{1}\textrm{--}\neutralino{1}$ pair
is produced by soft decays from pairs including $\chargino{1}$,
$\neutralino{2}$ or $\neutralino{1}$.
Although the $h$ and $Z$ bosons decay to many states, we target
$Z\rightarrow \ell\ell$ with
$h/Z\rightarrow bb/jj$.
We explore the parameters
$m(\neutralino{1})$ and $B(\neutralino{1} \rightarrow h \tilde{G})$ with fixed
$m(\chargino{1}, \neutralino{2}) - m(\neutralino{1}) = 1~\eV[G]$.
}
\label{fig:2ljets_signal_diagrams}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_sr_high_8_met_sig.pdf}
    \caption{SR-High-8}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_sr_llbb_mbb.pdf}
    \caption{SR-$\ell\ell bb$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_sr_int_met_sig.pdf}
    \caption{SR-Int}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_sr_low_met_sig.pdf}
    \caption{SR-Low}
\end{subfigure}
\caption{%
Example signal region histograms with benchmark signal sample yields overlaid
as dotted lines~\cite{atlas2022searches}.
Physically, signal yields would add on top of the backgrounds.
Data are shown; regions in the the top two plots observe zero data, and the
Poisson error bars for $0$ events are hidden for aesthetic reasons.
}
\label{fig:2ljets_signal_examples}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/2ljets_contours_c1n2.pdf}
\caption{%
Contours for the C1N2 model in the $\twoljets$ electroweak
analysis~\cite{atlas2022searches}.
Space below the solid red line is labelled as excluded and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
The yellow band shows the $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the prior distribution of the test statistic.
Grey areas are observed limits from the two-lepton parts
of~\cite{atlas_23l_SUSY_2016_24} and~\cite{atlas_2l_SUSY_2013_11}.
Exclusion is defined by the $95\%$ $\mathrm{CLs}$ prescription
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours_c1n2}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/2ljets_contours_gmsb.pdf}
\caption{%
Contours for the GMSB model in the $\twoljets$ electroweak
analysis~\cite{atlas2022searches}.
Space below the solid red line is labelled as excluded and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
The yellow band shows the $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the prior distribution of the test statistic.
Exclusion is defined by the $95\%$ $\mathrm{CLs}$ prescription
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours_gmsb}
\end{figure}

% upper limits
% definitely want this after pictures
\FloatBarrier
\begin{table}[tp]
\centering
% custom separator for aligned +-
% https://stackoverflow.com/a/2132998
\begin{tabular*}{\textwidth}{lr@{$~\pm~$}lccrrcc}
Region &
\multicolumn{2}{c}{Fitted} &
Data &
$\langle A\epsilon{ \sigma}\rangle_{\mathrm{obs}}^{95}~\mathrm{fb}$ &
$S_{\mathrm{obs}}^{95}$  &
$S_{\mathrm{exp}}^{95}$ &
$\mathrm{CLb}$ &
$p(s=0)$  \\[1.5ex]
DR-OffShell      & $22.1$ & $2.7$ & 21 & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50$ \\[.5ex]
DR-Low           & $22$ & $4$ & 18 & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50$ \\[.5ex]
DR-Int           & $35$ & $4$ & 38 & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23$ \\[.5ex]
DR-High          & $3.9$ & $0.5$  & 0  & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0.00$ & $0.50$ \\[.5ex]
DR-$\ell\ell bb$ & $0.51$ & $0.20$  & 0  & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50$ \\[.5ex]
\end{tabular*}
\caption{%
Upper limit results in $\twoljets$ electroweak discovery
regions~\cite{atlas2022searches}.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right:
the region name,
the post-fit background expectation,
the number of data observed,
the observed $95\%$ $\mathrm{CLs}$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
the expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central or
$\pm1$-sigma variations,
$\mathrm{CLb}$ evaluated with the signal expectation set to the observed upper limit,
and the discovery $p$-value (capped at $0.5$) with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test statistic.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided test.
All $p$-values are estimated by simulation of alternative data.
\TODO{add labels and references to asymptotic formulae paper}
\TODO{reference pdg rounding}
}
\label{tab:2ljets_discovery}
\end{table}

@@

Unsurprisingly, the strong part of the $\twoljets$ analysis is
detailed in Section~\ref{sec:2ljets_origins_strong} and
searches for effects from the strong sector.
It also uses conventional event variables, and focuses on features in the
distribution of the invariant masses of lepton pairs.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/2ljets_rjr_trees.pdf}
\caption{%
Decay trees for the $\twoljets$ RJR analysis~\cite{atlas2022searches}.
Both diagrams represent processes also targetted in the electroweak analysis.
(left) A fully-resolved decay tree with its particles labelled.
(right) Only the $Z\rightarrow\ell\ell$ (\underline{V}ector boson)
is resolved, but the supersymmetric system recoils off
hard QCD jets labelled ``ISR'', boosting the \underline{I}nvisible particles,
to generate visibly large $\met$ in models with small mass-splittings.
The same approach is used for SR-OffShell selections in the electroweak
analysis.
\emph{This figure was made by the RJR team.}
}
\label{fig:2ljets_rjr_decay_trees}
\end{figure}
